MacLeish

### 2021-07-19 README.Rmd
Trivial change

```{r, eval=FALSE, fig.width=7, fig.height=7, message=FALSE}
library(leaflet)
leaflet() %>%
  addTiles() %>%
  addPolygons(
    data = macleish_layers[["boundary"]], 
    weight = 1, fillOpacity = 0.1
  ) %>%
  addPolygons(
    data = macleish_layers[["buildings"]], 
    weight = 1, popup = ~ name
  ) %>%
  addPolylines(
    data = macleish_layers[["trails"]], 
    weight = 1, color = "brown",
    popup = ~ name
  ) %>%
  addPolylines(
    data = macleish_layers[["streams"]], 
    weight = 2
  ) %>%
  addMarkers(
    data = filter(macleish_layers[["landmarks"]], grepl("Met", Label)), 
    popup = ~Label
  )
```

>>>>

```{r, eval=FALSE, fig.width=7, fig.height=7, message=FALSE}
library(leaflet)
leaflet() %>%
  addTiles() %>%
  addPolygons(
    data = macleish_layers[["boundary"]], 
    weight = 1, fillOpacity = 0.1
  ) %>%
  addPolygons(
    data = macleish_layers[["buildings"]], 
    weight = 1, popup = ~ name
  ) %>%
  addPolylines(
    data = macleish_layers[["trails"]], 
    weight = 1, color = "brown",
    popup = ~ name
  ) %>%
  addPolylines(
    data = macleish_layers[["streams"]], 
    weight = 2
  ) %>%
  addMarkers(
    data = filter(macleish_layers[["landmarks"]], grepl("Met", Label)), 
    popup = ~Label
  )

```
